A Study on Online Sequential Learning using Bandits

### 2017-12-23 synopsis/intro1.tex
Latest on 23/12/2017

	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one arm and observe the reward associated with that ar. This reward is sampled from a probability  distribution associated with that specific arm. This game is repeated $T$ times and the goal of the learner is to maximize its profit by finding an action-selection strategy or policy that optimizes some long-term performance measure.

>>>>

	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one arm and observe the reward associated with that arm. This reward is sampled from a probability  distribution associated with that specific arm. This game is repeated $T$ times and the goal of the learner is to maximize its profit by finding an action-selection strategy or policy that optimizes some long-term performance measure.
